Modeling trend in temperature volatility using generalized LASSO

### 2018-05-13 nips-2018/paper.tex
add gitignore, PDIP algorithm

\usepackage{xcolor}
\newcommand{\alert}[1]{\textcolor{red}{TODO: #1}}

@@

\alert{explain the objective more. give the AR(1) example. Explain what you loses by this assumption (ACF,forecasting). Also explain that the covariace matrix is diagonal so it cannot capture the covariance structure. But incontrast to spatial stat literature, it does not make any assumption on estimated variances. Compare to Hallac et al and Lingren et al.}

As with~\eqref{eq:l1tf}, one can solve~\eqref{eq:l1tf_var} using the PDIP algorithm (as in, e.g., \texttt{cvxopt}~\citep{andersen_cvxopt:_2013}). First, we note that this is a generalized LASSO problem \citep{tibshirani_solution_2011}. The dual of a generalized LASSO with the objective $f(x)+\lambda \lVert Dx \lVert_1$ is: 
\begin{align}
\min_\nu&\quad f^*(-D^\top\nu) \\
\mbox{s.t.}&\quad \lVert \nu \lVert_\infty \le \lambda
\end{align}
 where $f^*(\cdot)$ is the Fenchel conjugate of $f$: $f^*(u)=\max_x u^tx-f(x)$. It is simple to show that 
\begin{equation}
f^*(\mathsf{u})=\sum_t (u_t-1)\log\frac{y_t^2}{1-u_t} + u_t-1.
\label{eq:conj}
\end{equation}

@@

@@

@@

>>>>

\usepackage{xcolor}
\newcommand{\attn}[1]{\textcolor{red}{TODO: #1}}
\newcommand{\one}{\mathbf{1}}
\renewcommand{\algorithmiccomment}[1]{\hfill $\rhd$ #1}

@@

\attn{explain the objective more. give the AR(1) example. Explain what you loses by this assumption (ACF,forecasting). Also explain that the covariace matrix is diagonal so it cannot capture the covariance structure. But incontrast to spatial stat literature, it does not make any assumption on estimated variances. Compare to Hallac et al and Lingren et al.}

As with~\eqref{eq:l1tf}, one can solve~\eqref{eq:l1tf_var} using the PDIP algorithm (as in, e.g., \texttt{cvxopt}~\citep{andersen_cvxopt:_2013}). First, we note that this is a generalized LASSO problem \citep{tibshirani_solution_2011}. The dual of a generalized LASSO with the objective $f(x)+\lambda \lVert Dx \lVert_1$ is: 
\begin{align}
\min_\nu&\quad f^*(-D^\top\nu) \\
\mbox{s.t.}&\quad \lVert \nu \lVert_\infty \le \lambda
\end{align}
 where $f^*(\cdot)$ is the Fenchel conjugate of $f$: $f^*(u)=\max_x u^tx-f(x)$. It is simple to show that 
\begin{equation}
f^*(\mathsf{u})=\sum_t (u_t-1)\log\frac{y_t^2}{1-u_t} + u_t-1.
\label{eq:conj}
\end{equation}
Writing
\[
  r_w(v,\mu_1,\mu_2):=
  \begin{bmatrix}
    \nabla f^*(-D^\top v) + D(v-\lambda \one)^\top \mu_1 -
    D(v+\lambda \one)^\top \mu_2\\
    -\mu_1(v-\lambda\one)+\mu_2(v + \lambda\one) -w^{-1}\one
  \end{bmatrix}
  =
  \begin{bmatrix}
  0\\0\end{bmatrix}
\]
for $w>0$, where $\mu_1$ and $\mu_2$ are dual variables for the $\ell_\infty$ constraint in the dual problem. As $w\rightarrow\infty$, the solution to this nonlinear system reduces to the KKT conditions. Therefore, the PDIP method takes Newton steps to solve the system for a series of increasing values of $w$. \autoref{alg:pdip} provides the details.
\begin{algorithm}
  \caption{PDIP for $\ell_1$ variance estimation}
  \label{alg:pdip}
  \begin{algorithmic}
    \REQUIRE $\lambda>0$, $w>0$, $\nu\leftarrow 0$, $\mu_1\leftarrow 0$, $\mu_2\leftarrow 0$, $J\in\mathbb{Z}^+$, $\{w_k\}$ \COMMENT{Initialization}
    \FOR[Central path]{$k=1,2,\ldots$}
    \FOR[Newton updates]{$j=1,\ldots,J$}
    \STATE Solve $A [\Delta\nu\; \Delta\mu_1\; \Delta\mu_2]^\top=r^j_{w_k}$ to find the search direction.
    \STATE $\quad\quad A$ is the Jacobian of $r_w$.
    \STATE Update $r^{j+1} \leftarrow r^j + [\Delta\nu\; \Delta\mu_1\; \Delta\mu_2]^\top$.
    \ENDFOR
   \ENDFOR
   \RETURN $h=-D^\top\nu$ \attn{Is this right??}
  \end{algorithmic}
\end{algorithm}

@@

\attn{Detailed discussion of the PDIP to here}

@@

\attn{Redo the below and move to the section on PDIP above}

@@

\attn{Make this a theorem}
